### 2020-04-14 README.Rmd
rm old badges

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/bgreenwell/pdp?branch=master&svg=true)](https://ci.appveyor.com/project/bgreenwell/pdp)
[![Codecov test coverage](https://codecov.io/gh/bgreenwell/pdp/branch/master/graph/badge.svg)](https://codecov.io/gh/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)

>>>>

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![R build status](https://github.com/bgreenwell/pdp/workflows/R-CMD-check/badge.svg)](https://github.com/bgreenwell/pdp/actions)
[![Codecov test coverage](https://codecov.io/gh/bgreenwell/pdp/branch/master/graph/badge.svg)](https://codecov.io/gh/bgreenwell/pdp?branch=master)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
